\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup

### 2025-03-21 code/paper.qmd
reduced visuals, expanded and edited interpretations, wrote conclusion

library(readxl)
library(viridis)
library(ggthemes)
library(tidytext)
library(knitr)
library(tidyverse)

# path to repo
#repo_path <- str_c(~/Desktop/UMICH/SURV622_Assignment/data/") # felix
repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin

@@

@@

Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
The highest peak is around lunchtime, likely due to people posting during their lunch break.
There is also significant activity in the afternoon, evening, and early morning.
This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
The trend for comments (see Figure 4) mirrors that of posts.
This makes sense because people are likely using Reddit at similar times for both posting and commenting.
However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

```{r}
posts_data_clean |> 
  group_by(hour_posted ) |> 
  reframe(Total = n()) |> 
  ggplot(aes(x=hour_posted, y=Total)) + 
  # geom_bar(stat = "identity", fill = "steelblue") + 
  geom_point(color = "blue", size = 3) +  
  geom_line(color = "steelblue", linewidth = 1) +
  labs(
    title = "Figure 3. Total Number of Posts by Hour of Day",
    subtitle = "(24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal() +
  theme_hc()

comments_data_clean |> 
  group_by(hour_posted ) |> 
  reframe(Total = n()) |> 
  ggplot(aes(x=hour_posted, y=Total)) + 
  # geom_bar(stat = "identity", fill = "steelblue") + 
  geom_point(color = "green", size = 3) +  
  geom_line(color = "lightgreen", linewidth = 1) +
  labs(
    title = "Figure 4. Total Number of Comments by Hour of Day",
    subtitle = "(24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_hc()
```

### What are the words in the set of posts you have assembled that appear most frequently?

```{r}
#| fig-width: 6
#| fig-height: 7
#| 
# tokenize words to count frequencies for reddit posts
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Posts (Including Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()

# tokenize words to count frequencies for reddit comments
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "lightgreen") +  # Removed extra parentheses
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Comments (Including Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()
```

The graphs above show the most frequent words in both Reddit posts and their comments.
However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions.
To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.

### How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?

```{r}
#| fig-width: 6
#| fig-height: 7
#| #| 
# tokenize words to count frequencies for reddit posts removing stop words
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Posts (Removing Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()

# tokenize words to count frequencies for Reddit comments, removing stop words
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 50)

# plot
ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "lightgreen") +  # Removed extra parentheses
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Comments (Removing Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()
```

The graphs above show the most frequent words used in both Reddit posts and their comment sections.
We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.

*Coding Comments*.
We coded 400 comments chosen at random

@@

>>>>

library(readxl)
library(viridis)
library(ggthemes)
library(tidytext)
library(knitr)
library(tidyverse)
library(patchwork)

# path to repo
repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
# repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin

@@

*Post and Comment Trends*

@@

*Word Frequency*

Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
The highest peak is around lunchtime, likely due to people posting during their lunch break.
There is also significant activity in the afternoon, evening, and early morning.
This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
The trend for comments (see Figure 3) mirrors that of posts.
This makes sense because people are likely using Reddit at similar times for both posting and commenting.
However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

```{r}
# Aggregate posts data
posts_by_hour <- posts_data_clean |> 
  group_by(hour_posted) |> 
  reframe(Total = n()) |> 
  mutate(type = "Posts")

# Aggregate comments data
comments_by_hour <- comments_data_clean |> 
  group_by(hour_posted) |> 
  reframe(Total = n()) |> 
  mutate(type = "Comments")

# Combine both datasets
combined_data <- bind_rows(comments_by_hour, posts_by_hour)

# Plot with facet_wrap to display them side by side
ggplot(combined_data, aes(x = hour_posted, y = Total)) + 
  geom_point(aes(color = type), size = 3) +  
  geom_line(aes(color = type), linewidth = 1) +
  scale_color_manual(values = c("Posts" = "steelblue", "Comments" = "lightgreen")) +  # Color distinction
  facet_wrap(~type, scales = "free_y") +  # Display side by side
  labs(
    title = "Figure 3. Total Number of Posts and Comments by Hour",
    subtitle = "(24-hour clock)",
    x = "Hour of Day",
    y = "Total Count"
  ) +
  theme_minimal() +
  theme_hc() +
  theme(legend.position = "none") 
```

The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections. These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms. From the visualizations, we can see that many of these words are directly related to our topic of discussion. Specifically, there are frequent mentions of 'President,' 'DOGE,' 'federal government,' and 'RIF,' which suggest that discussions surrounding political events, cryptocurrency (like Dogecoin), and government-related issues are significant in the posts and comments. This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.

```{r}
# Tokenize words and count frequencies for Reddit posts
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 25)

# Tokenize words and count frequencies for Reddit comments
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 25)

# Plot for posts
plot_posts <- ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(x = "Word",
       y = "Count") +
  theme_minimal()

# Plot for comments
plot_comments <- ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "lightgreen") +
  coord_flip() +
  labs(x = "Word",
       y = "Count") +
  theme_minimal()

# Combine them side by side using patchwork
combined_plot <- plot_posts + plot_comments + plot_layout(ncol = 2) + plot_annotation(title = "Figure 4. Top 25 Words in Reddit Posts and Comments")

# Display the combined plot
combined_plot

*Coding Comments*

We randomly selected and coded 400 comments from the Reddit posts. The table below shows the distribution of favorability coding for these comments. Among the 400 comments, the majority (217) expressed opposition to DOGE's approach to reducing the federal workforce, while 110 were supportive, and 73 remained neutral. A large number of comments (12,153) were not coded, as their content was not relevant for favorability assessment.

@@

## Conclusion

In this study, we explored the impact of the Department of Government Efficiency’s (DOGE) actions on federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse. By examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public. Our findings indicate that these discussions are heavily influenced by political events and high-profile figures, such as President Trump and Elon Musk, with particular attention given to DOGE’s controversial cost-cutting measures. Through the analysis of both posts and comments, we captured a wide range of reactions, with the majority being strongly opposed to DOGE’s approach. The frequent mention of terms like ‘President,’ ‘DOGE,’ ‘federal government,’ and ‘RIF’ underscores the community’s focus on government policies and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217 out of 400 were opposed to DOGE’s approach, 110 were supportive, and 73 were neutral. Additionally, patterns in post volume, especially peaks during significant news events, highlight the dynamic nature of these discussions, providing insights into the timing and public reactions to key policy decisions. While our study provides a snapshot of Reddit discussions during a specific period, the findings demonstrate the value of social media platforms like Reddit in capturing public sentiment on contemporary political and policy issues. However, it’s important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.

Furthermore, the use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification. The specific subreddits analyzed, while designed to capture diverse perspectives, may still over-represent certain political or ideological viewpoints. Additionally, the relatively short timeframe of this analysis—spanning only March 2-10, 2025—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold. Future research could address these limitations by expanding the data collection to other platforms or a longer timeframe and by incorporating demographic data to better understand the views of different Reddit user groups.

### 2025-03-21 code/paper.tex
reduced visuals, expanded and edited interpretations, wrote conclusion

@@

Most posts occur during the early morning, noon, and afternoon hours
(see Figure 3). The highest peak is around lunchtime, likely due to
people posting during their lunch break. There is also significant
activity in the afternoon, evening, and early morning. This could be
because people have more free time or stay up late, allowing them to
take the time to write posts, which require more effort than quick
interactions. The fewest posts are seen in the morning, which makes
sense as people are typically getting ready for work, commuting, or
sleeping in. The trend for comments (see Figure 4) mirrors that of
posts. This makes sense because people are likely using Reddit at
similar times for both posting and commenting. However, the volume of
comments is much higher than the number of posts, as each post receives
many comments from different users.

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-2.pdf}

\subsection{What are the words in the set of posts you have assembled
that appear most
frequently?}\label{what-are-the-words-in-the-set-of-posts-you-have-assembled-that-appear-most-frequently}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-2.pdf}

The graphs above show the most frequent words in both Reddit posts and
their comments. However, many of these words are stopwords, which don't
provide much insight into the actual content of the discussions. To get
a better understanding of what people are really talking about, we will
remove these stopwords in the next step.

\subsection{How does this change if you exclude ``stop words'' such as
``a,'' ``an,'' ``the,'' ``is,'' and others that are common in English
sentences but are generally not
informative?}\label{how-does-this-change-if-you-exclude-stop-words-such-as-a-an-the-is-and-others-that-are-common-in-english-sentences-but-are-generally-not-informative}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-1.pdf}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-2.pdf}

The graphs above show the most frequent words used in both Reddit posts
and their comment sections. We can see that many of these words are
directly related to our topic, with frequent mentions of the President,
DOGE, the federal government, and RIF.

\emph{Coding Comments}. We coded 400 comments chosen at random

@@

>>>>

\emph{Post and Comment Trends}

@@

\emph{Word Frequency}

Most posts occur during the early morning, noon, and afternoon hours
(see Figure 3). The highest peak is around lunchtime, likely due to
people posting during their lunch break. There is also significant
activity in the afternoon, evening, and early morning. This could be
because people have more free time or stay up late, allowing them to
take the time to write posts, which require more effort than quick
interactions. The fewest posts are seen in the morning, which makes
sense as people are typically getting ready for work, commuting, or
sleeping in. The trend for comments (see Figure 3) mirrors that of
posts. This makes sense because people are likely using Reddit at
similar times for both posting and commenting. However, the volume of
comments is much higher than the number of posts, as each post receives
many comments from different users.

@@

The graphs below (Figure 4) show the most frequent words used in both
Reddit posts and their comment sections. These words were identified by
tokenizing the text and removing stop words, then counting the
occurrences of the most common terms. From the visualizations, we can
see that many of these words are directly related to our topic of
discussion. Specifically, there are frequent mentions of `President,'
`DOGE,' `federal government,' and `RIF,' which suggest that discussions
surrounding political events, cryptocurrency (like Dogecoin), and
government-related issues are significant in the posts and comments.
This highlights the focus of the community on these key themes,
reflecting the ongoing conversations and interests of Reddit users
within this context.

@@

\emph{Coding Comments}

We randomly selected and coded 400 comments from the Reddit posts. The
table below shows the distribution of favorability coding for these
comments. Among the 400 comments, the majority (217) expressed
opposition to DOGE's approach to reducing the federal workforce, while
110 were supportive, and 73 remained neutral. A large number of comments
(12,153) were not coded, as their content was not relevant for
favorability assessment.

@@

\section{Conclusion}\label{conclusion}

In this study, we explored the impact of the Department of Government
Efficiency's (DOGE) actions on federal workers' perceptions of job
security, using Reddit as a platform to analyze public discourse. By
examining Reddit posts and comments related to DOGE's workforce
reduction policies, we gained valuable insights into the sentiments of
both federal workers and the broader public. Our findings indicate that
these discussions are heavily influenced by political events and
high-profile figures, such as President Trump and Elon Musk, with
particular attention given to DOGE's controversial cost-cutting
measures. Through the analysis of both posts and comments, we captured a
wide range of reactions, with the majority being strongly opposed to
DOGE's approach. The frequent mention of terms like `President,' `DOGE,'
`federal government,' and `RIF' underscores the community's focus on
government policies and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217
out of 400 were opposed to DOGE's approach, 110 were supportive, and 73
were neutral. Additionally, patterns in post volume, especially peaks
during significant news events, highlight the dynamic nature of these
discussions, providing insights into the timing and public reactions to
key policy decisions. While our study provides a snapshot of Reddit
discussions during a specific period, the findings demonstrate the value
of social media platforms like Reddit in capturing public sentiment on
contemporary political and policy issues. However, it's important to
note that Reddit may not fully represent the broader population's views,
as the platform tends to skew younger and more politically engaged,
potentially limiting the generalizability of these findings.

Furthermore, the use of sentiment analysis on social media presents
challenges, as it can be influenced by sarcasm, humor, or polarized
language, which might affect the accuracy of sentiment classification.
The specific subreddits analyzed, while designed to capture diverse
perspectives, may still over-represent certain political or ideological
viewpoints. Additionally, the relatively short timeframe of this
analysis---spanning only March 2-10, 2025---means that we may not have
captured long-term trends or shifts in sentiment as the DOGE policies
unfold. Future research could address these limitations by expanding the
data collection to other platforms or a longer timeframe and by
incorporating demographic data to better understand the views of
different Reddit user groups.
